Adaptive Scheduling of Scientific Workflows\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-05-07 main.tex
description of 3 pc cluster

    To test various settings, we also vary the cluster configuration and consider
    variants of the default cluster presented above:\\
    $\bullet$ {\em Small} and {\em large} clusters. While the default cluster consists of 36 nodes (6 of each kind), we
    consider a small cluster with one processor of each kind ($6$ processors in total), and a
    large cluster with ten processors of each kind ($60$ processors in total). \skug{leaving the big cluster inside for
    the case we do want to include it}\\
    $\bullet$ {\em Fat-and-thin} cluster. In this cluster, the fastest processors have the smallest amount of memory (thin),
    while the slowest processors have the largest memories (fat).
    The overall amount of memory in the cluster, as well as the overall speed of all processors remain the same as in the
            {\em normal} cluster.
%\end{itemize}

@@

    \subsubsection{Impact of cluster size}
    On a cluster with only 6 processors (1 of each kind), the baseline makes more failures: from $43.4$\%  (small workflows)
    to $88.9$\% (mid-sized) and $94.4$\% (big workflows).
    These values also become more unattainable: the makespans heuristics produce are worse by $3-12$\% (\heftbl) to $12-52$\%
    (\heftmm).
    However, these comparisons are less expressive, because most of baseline solutions are invalid.
    \skug{TODO: add numbers about failures on the small cluster with the fixed bug}

>>>>

    To test various settings, we also vary the cluster configuration and consider
    variants of the default cluster presented above:\\
    $\bullet$ {\em Small} and {\em large} clusters. While the default cluster consists of 36 nodes (6 of each kind), we
    consider a small cluster with three processors of each kind ($18$ processors in total), and a
    large cluster with ten processors of each kind ($60$ processors in total). \skug{leaving the big cluster inside for
    the case we do want to include it}\\
    $\bullet$ {\em Fat-and-thin} cluster. In this cluster, the fastest processors have the smallest amount of memory (thin),
    while the slowest processors have the largest memories (fat).
    The overall amount of memory in the cluster, as well as the overall speed of all processors remain the same as in the
            {\em normal} cluster.
%\end{itemize}

@@

    \subsubsection{Impact of cluster size}
    On a cluster with only $18$ processors ($3$ of each kind), the baseline makes more failures: from $43.8$\%  (small workflows)
    to $77.8$\% (mid-sized) and $88.9$\% (big workflows).
    At the same time, each heuristic is unable to schedule one big workflow and one middle-sized one.
    On the workflows that they are able to schedule, \heftbl and \heftblc produce makespans that are $<1$\% bigger than
    those of the baseline on small and middle-sized workflows.
    On the big workflows, they produce makespans that are $3.5$\% and $2.3$\% bigger respectively.
    The performance of \heftmm improves more with workflow size: it goes from producing $16$\% bigger makespans on small
    workflows, to $8$\% on middle-sized ones, to $7$\% on big workflows.

   Like in the normal cluster, \heftmm again consistently shows smaller peak memory usage in the cluster.
    It utilizes on average $15$\% of memory on small workflows ($17.7$\% for \heftbl and \heftblc),
    $31$\% on middle-sied workflows ($45.2$\% and $44.9$\% on \heftbl and \heftblc, respectively),
    and $34$\% on big workflows ($50.1$\% and $50.2$\% for \heftbl and \heftblc).
